### 2019-06-24 README.Rmd
removed rownames from pathEnrich table in README

```{r pathEnrich}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
knitr::kable(head(sig_pe),
             caption = "Table 1. Head of sig_pe dataframe generated using pathEnrich") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

>>>>

```{r pathEnrich}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
knitr::kable(head(sig_pe),
             caption = "Table 1. Head of sig_pe dataframe generated using pathEnrich", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```
